### 2024-01-09 paper/si_4_others.tex
major cleanup: flat out dirs as per arxiv request

The illustrations of CNN architecture displayed in Figure 1 of the main text,
as well as  Supplementary Figure 21 and Supplementary Figure 30,
were obtained from the GitHub repository dair-ai/ml-visuals \cite{Saravia_ML_Visuals_2021}.
Blender was used to create and render the visual representation of the catalyst analysis pipeline shown in Figure 1 of the main text.

>>>>

The illustrations of CNN architecture displayed in Figure 1 of the main text,
as well as \cref{si_fig21:occlusion} and \cref{si_fig30:shifting},
were obtained from the GitHub repository dair-ai/ml-visuals \cite{Saravia_ML_Visuals_2021}.
Blender was used to create and render the visual representation of the catalyst analysis pipeline shown in Figure 1 (TODO: cross-ref) of the main text.
